*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-15 Code/Manuscript_O2.Rmd
intro subheadings

## Mireille
### Chapter 1 General Intro

@@

*Prochlorococcus marinus* comprises many strains, organized into clades, defined by 16S-23S intergenic transcribed ribosomal sequence signatures (Rocap et al., 2003). The various clades inhabit distinct ecological niches [@moorePhysiologyMolecularPhylogeny1998], originally defined by Low Light or High Light.  Of at least 12 known *Prochlorococcus* clades only 5 to date have cultured representatives; HLI, HLII, LLI, LLII/III and LIV [@billerProchlorococcusStructureFunction2015].

@@

@@

>>>>

## *Prochlorococcus* evolutionary and functional diversity

@@

*Prochlorococcus marinus* comprises many strains, organized into clades, defined by 16S-23S intergenic transcribed ribosomal sequence signatures (Rocap et al., 2003). The clades inhabit distinct ecological niches [@moorePhysiologyMolecularPhylogeny1998], originally defined by Low Light or High Light.  Of at least 12 known *Prochlorococcus* clades only 5 to date have cultured representatives; HLI, HLII, LLI, LLII/III and LIV [@billerProchlorococcusStructureFunction2015].

@@

## *Prochlorococcus* responses to changing niches

@@

## Photosystem II maintenance as a limitation on *Prochlorococcus* growth
